Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 paper.tex
Final revisions to paper

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar} \textbf{, a friends-of-friends like algorithm which adaptively refines in six phase-space dimensions and one time dimension}. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. \textbf{For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the Pop III stars, it only shifts our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog. \textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First, \textbf{36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

@@

There has been a large amount of work done throughout the literature investigating the relationship between the LW background intensity and halo masses. \citet{Tegmark97} numerically integrated a chemical network to calculate the minimum mass a halo must have in order to cool, by considering \hh{} formation and cooling rates. They conclude that cooling by \hh{} is efficient and leads to the first formation of structures. They found a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift. At $z = 15$, this minimum halo mass is $10^{6} M_{\odot}$. \citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment. They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the LSST to see these regions of the universe. They used the minimum halo mass capable of cooling via \hh{} from \citet{Trenti09_SFR} as one part of their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background). Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}). For a LW background of $J_{\rm LW} / J_{21} = 0.2$, we see halos hosting Pop III stars down to $4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger. Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background. \textbf{\citet{Visbal14} used zero-dimensional one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background. They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to withing a factor of two. This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at a redshift of 20. At that redshift, almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above. \citet{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.}\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6. They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding. They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ at $z = 20$, similar to results from \citet{Tegmark97}. The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citep[see][]{Wise07_UVB, OShea08}. It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies. For example, at late times, a single galaxy dominates the LW radiation field, and drives up the host halo masses. However, we would expect this to happen at different times in other cosmological volumes. Therefore, we cannot directly compare the time dependence, however, a comparison as a function of LW intensity is still valid.

\citet{Yoshida03} used cosmological simulations to study the formation of primordial star-forming clouds. They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds. Importantly, they included \hh{} self-shielding within halos. In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12). They found that in the presence of a LW background of 0.01 J$_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$. When \hh{} self-shielding is taken into account along with a LW background, their minimum halo mass decreases to $4.5 \times 10^{5} M_{\odot}$. This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$. They found that \hh{} self-shielding does appear to be an efficient mechanism enabling primordial gas cooling. In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$. While our halos never experience a LW intensity as low as 0.01 J$_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}). \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background. They found that \hh{} cooling is dominant even when there is a large LW background present. They did not include self-shielding and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}). Their J$_{\rm LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$. \citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds. They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse. They also ignored \hh{} self-shielding in their calculations which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares). Their halo masses are similar to the results of \citet{Wise07_UVB}. Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$. \textbf{\citet{Hirano15} used cosmological simulations to study 1540 gas clouds in the early universe to derive the corresponding primordial stellar mass distribution. They find that star forming halos of virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at z = 30 and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at z = 10. These masses are fairly similar to our work, with our mean halo mass lying between these values.}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at z=20, the purple solid line from \citet{Visbal14} at z=20,}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$. The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.}
    \label{fig:compare_JLW_mass}
\end{figure}

@@

There are a few minor shortcomings to this work that should be noted. \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo. In the near-field with an ionisation front breaking out of a halo, they find that the LW escape fraction is greater than 95\%. But when the ionisation front is contained within the halo, they found that the LW escape fraction can range from 3\% to 88\%. In general, they find that the LW escape fractions in the far-field are higher than 75\%. \textbf{Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations. They find similar results as \citet{Schauer17}, with the exception that H2 shielding by neutral hydrogen decreases escape fractions as compared to when only H2 shielding is considered. In their more recent work, they find that this difference in escape fractions between when H2 shielding by neutral hydrogen is included or not is negligible. \citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code. They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.} Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation. We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.

We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}. Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time. Pop III star formation is delayed by an average of $\delta z = 4$ by increasing the halo mass needed to overcome the bulk velocity by about a factor of three \citep{Greif11_Delay}. The streaming velocities will generally result in lower gas densities within halos as well as an offset of the peak density from the center of the halo \citep{OLeary12}. Often in the literature, streaming velocities are only studied for a few halos. But \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands). These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the star forming halos in our simulation. \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos. Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).  In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.  Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results. \textbf{\citet{Schauer19} quote minimum and average halo masses necessary for the center of the halo to have enough cold dense gas available for star formation for various streaming velocities to study star formation in minihalos and it's relation to the 21-cm absorption feature from the EDGES survey. Ranging from 0 $\rm v_{\rm bc}$ to 3.0 $\rm v_{\rm bc}$ in units of $\sigma_{\rm rms}$, they found that the minimum halo mass ranges from $5 \times 10^5 M_{\odot}$ to $10^7 M_{\odot}$, and the average halo mass ranges from about $2 \times 10^6 M_{\odot}$ to $4 \times 10^7 M_{\odot}$. Our halo masses generally fall within these ranges, confirming again that streaming velocities would likely not affect our results.}

@@

JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
HST-AR-14326.  We thank the support staff at Georgia Tech's PACE,
where we ran this simulation.  The freely available plotting library
{\sc matplotlib} \citep{matplotlib} was used to construct numerous
plots within this paper. Computations and analysis described in this
work were performed using the publicly-available \enzo{} and \yt{}
codes, which is the product of a collaborative effort of many
independent scientists from numerous institutions around the world.

>>>>

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, \textbf{an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.} The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. \textbf{For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog. \textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First \textbf{given our assumed IMF (Equation \ref{IMF}), 36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

@@

There has been a large amount of work done throughout the literature investigating the relationship between the LW background intensity and halo masses. \citet{Tegmark97} numerically integrated a chemical network to calculate the minimum mass a halo must have in order to cool, by considering \hh{} formation and cooling rates. They conclude that cooling by \hh{} is efficient and leads to the first formation of structures. They found a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift. At $z = 15$, this minimum halo mass is $10^{6} M_{\odot}$. \citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment. They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the LSST to see these regions of the universe. They used the minimum halo mass capable of cooling via \hh{} from \citet{Trenti09_SFR} as one part of their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background). Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}). For a LW background of $J_{\rm LW} / J_{21} = 0.2$, we see halos hosting Pop III stars down to $4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger. Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background. \textbf{\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background. They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to within a factor of two. This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at redshift 20. Here almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above. \citeauthor{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.} \citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6. They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding. They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ at $z = 20$, similar to results from \citet{Tegmark97}. The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citep[see][]{Wise07_UVB, OShea08}. It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies. For example, at late times, a single galaxy dominates the LW radiation field, and drives up the host halo masses. However, we would expect this to happen at different times in other cosmological volumes. Therefore, we cannot directly compare the time dependence, however, a comparison as a function of LW intensity is still valid.

\citet{Yoshida03} used cosmological simulations to study the formation of primordial star-forming clouds. They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds. Importantly, they included \hh{} self-shielding within halos. In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12). They found that in the presence of a LW background of 0.01 J$_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$. When \hh{} self-shielding is taken into account along with a LW background, their minimum halo mass decreases to $4.5 \times 10^{5} M_{\odot}$. This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$. They found that \hh{} self-shielding does appear to be an efficient mechanism enabling primordial gas cooling. In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$. While our halos never experience a LW intensity as low as 0.01 J$_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}). \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background. They found that \hh{} cooling is dominant even when there is a large LW background present. They did not include self-shielding and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}). Their J$_{\rm LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$. \citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds. They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse. They also ignored \hh{} self-shielding in their calculations which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares). Their halo masses are similar to the results of \citet{Wise07_UVB}. Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$. \textbf{\citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution. They find that stars form in halos above virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at $z = 30$ and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at $z = 10$. These masses are consistent with our results with our mean halo mass lying between these values.}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$. The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.}
    \label{fig:compare_JLW_mass}
\end{figure}

@@

There are a few minor shortcomings to this work that should be noted. \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo. In the near-field with an ionisation front breaking out of a halo, they find that the LW escape fraction is greater than 95\%. But when the ionisation front is contained within the halo, they found that the LW escape fraction can range from 3\% to 88\%. In general, they find that the LW escape fractions in the far-field are higher than 75\%. \textbf{Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations. They find similar results as \citet{Schauer17}, with the exception that \hh{} shielding by neutral hydrogen decreases LW escape fractions as compared to when only \hh{} shielding is considered. In their more recent work, they find that this difference in LW escape fractions between when \hh{} shielding by neutral hydrogen is included or not is negligible. \citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code. They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.} Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation. We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.

We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}. Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time. Pop III star formation is delayed by an average of $\delta z = 4$ by increasing the halo mass needed to overcome the bulk velocity by about a factor of three \citep{Greif11_Delay}. The streaming velocities will generally result in lower gas densities within halos as well as an offset of the peak density from the center of the halo \citep{OLeary12}. Often in the literature, streaming velocities are only studied for a few halos. But \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands). These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the star forming halos in our simulation. \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos. Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).  In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.  Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results. \textbf{\citet{Schauer19} give minimum and average halo masses necessary for enough cold dense gas to form in halo centers to support star formation for various streaming velocities in their study of star formation in minihalos and its relation to the EDGES 21-cm absorption feature \citep{EDGES}. Ranging from 0 $\rm v_{\rm bc}$ to 3.0 $\rm v_{\rm bc}$ in units of $\sigma_{\rm rms}$, they found that the minimum halo mass ranges from $5 \times 10^5 M_{\odot}$ to $10^7 M_{\odot}$, and the average halo mass ranges from about $2 \times 10^6 M_{\odot}$ to $4 \times 10^7 M_{\odot}$. Our halo masses generally fall within these ranges, confirming again that only the rarest and strongest of the streaming velocities would affect our results.}

@@

JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.  The freely available plotting library {\sc matplotlib} \citep{matplotlib} was used to construct numerous plots within this paper. Computations and analysis described in this work were performed using the publicly-available \enzo{} and \yt{} codes, which is the product of a collaborative effort of many independent scientists from numerous institutions around the world.
